Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-23 paper/paper.tex
footnotes acting funky, but look fine, so whatever for now
changed order of wingmen/centerman off, as per adrien

The team is made of 12 Rutgers undergraduates
% List, can we do itemize for this? two columns? needs to be smaller

@@

\newpage
\appendix
\renewcommand\thesection{Appendix \Alph{section}}
\section{Pre-flight Procedures}
\begin{enumerate}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
	\item Assemble plane.
	\item Check all mechanical and electrical connections.
		\begin{itemize}
		\itemspace
		\item Are all nuts/bolts loc-tited?
		\item Are all servo extentions connected and properly secured?
		\item Are all access hatches secured?
		\end{itemize}
	\item Position wingmen*, centerman**.
	\item Pilot turns on transmitter, announces ``transmitter on.''
	\item Pilot requests ``reciever on''.  Centerman turns on reciever, acknowledges.
	\item Pilot completes surface checks:
		\begin{itemize}
		\itemspace
		\item Ailerons
		\item Elevator
		\item Rudder
		\item Throttle
		\end{itemize}
	\item Prime engine.
	\item Pilot obtains visual and verbal confirmation that wingmen, centerman are in place and alert.
	\item Pilot requests ``ignition on.''  Centerman moves ignition switch to the ``on'' position and acknowledges.
	\item Starter requests ``prop clear.''  Starter obtains visual confirmation that no person is standing in the prop arc and announces ``prop clear.''
	\item Starter announces ``contact'' and starts the engine.
	\item Starter clears the area.
	\item Pilot repeats surface and throttle checks at close range.
	\item Pilot leaves starting area and performs surface and throttle checks from a distance (range test).
	\item Pilot returns to starting area to prepare for taxi.
	\item Pilot requests ``wingmen off.''  Wingmen carefully clear the area and acknowledge.
	\item Pilot requests ``centerman off.''  Centerman carefully clears the area and acknowledge.
	\item Pilot taxis airplane to appropriate location to begin takeoff.
	\item Pilot commences takeoff.

@@

>>>>

The team is made of 10 Rutgers undergraduates
% List, can we do itemize for this? two columns? needs to be smaller

@@

\newpage
\appendix
\renewcommand\thesection{Appendix \Alph{section}}
\section{Pre-flight Procedures}
\begin{enumerate}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
	\item Assemble plane.
	\item Check all mechanical and electrical connections.
		\begin{itemize}
		\itemspace
		\item Are all nuts/bolts loc-tited?
		\item Are all servo extentions connected and properly secured?
		\item Are all access hatches secured?
		\end{itemize}
	\item Position wingmen\footnotemark, centerman\footnotemark.
	\item Pilot turns on transmitter, announces ``transmitter on.''
	\item Pilot requests ``reciever on''.  Centerman turns on reciever, acknowledges.
	\item Pilot completes surface checks:
		\begin{itemize}
		\itemspace
		\item Ailerons
		\item Elevator
		\item Rudder
		\item Throttle
		\end{itemize}
	\item Starter primes engine.
	\item Pilot obtains visual and verbal confirmation that wingmen, centerman are in place and alert.
	\item Pilot requests ``ignition on.''  Centerman moves ignition switch to the ``on'' position and acknowledges.
	\item Starter requests ``prop clear.''  Starter obtains visual confirmation that no person is standing in the prop arc and announces ``prop clear.''
	\item Starter announces ``contact'' and starts the engine.
	\item Starter clears the area.
	\item Pilot repeats surface and throttle checks at close range.
	\item Pilot leaves starting area and performs surface and throttle checks from a distance (range test).
	\item Pilot returns to starting area to prepare for taxi.
	\item Pilot requests ``centerman off.''  Centerman carefully clears the area and acknowledges.
	\item Pilot requests ``wingmen off.''  Wingmen carefully clear the area and acknowledge.
	\item Pilot taxis airplane to appropriate location to begin takeoff.
	\item Pilot commences takeoff.

@@

\footnotetext[1]{Two men, one positioned at each wing tip, preventing the plane from moving during engine start and subsequent surface checks.}
\footnotetext{Man straddling the fuse, preventing the plane from moving during engine start and subsequent surface checks}
